---
title: "Untitled"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(car)
```

```{r}
getwd()

data1 = read.csv(file="InterseedingSurveyLFFRb.csv")
str(data1)
```
# Who took the survey?
```{r}
Q1 = data1 %>%
  count(I.am, sort= TRUE) %>%
  rename("Type" = "I.am") %>%
  mutate(Type= fct_recode(Type,
             "Farmer" = "Farmer",
             "Agribusiness Employee" = "Agribusiness",
             "Agency/University Employbee" = "Agency/University")) 


```

```{r}
Q1_plot = Q1 %>%
  ggplot(aes(x = Type, y = n, fill= Type, label= n)) +
  geom_col() +
  geom_text(nudge_y= 2) +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  labs(title= "I am a:") +
  coord_flip()

Q1_plot
```


# Do you plant (recommend planting) cover crops into or after corn silage/grain? (Mark all that apply)
```{r}
Q2 = data1 %>%
  count(Do.you, sort= TRUE) %>%
  rename("Response" = "Do.you")
  
```

```{r}
Q2_plot = Q2 %>%
  ggplot(aes(x = Response, y = n, fill= Response, label= n)) +
  geom_col() +
  geom_text(nudge_y= 2) +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  labs(title= "Do you plant (recommend planting) cover crops into or after corn silage/grain? (Mark all that apply)") +
  coord_flip()

Q2_plot
```


# Why do you plant (recommend planting) cover crops into or after corn silage/grain? (Mark all that apply)
```{r}
Q3 = data1 %>%
  count(Why, sort= TRUE) %>%
  rename("Response" = "Why")
  
```

```{r}
Q3_plot = Q3 %>%
  ggplot(aes(x = Response, y = n, fill= Response, label= n)) +
  geom_col() +
  geom_text(nudge_y= 2) +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  labs(title= "Why do you plant (recommend planting) cover crops into or after corn silage/grain? (Mark all that apply)") +
  coord_flip()

Q3_plot
```

# Which cover crop species do you plant (recommend planting) after corn silage harvest? (Circle all that apply)
```{r}
Q4 = data1 %>%
  count(Interseed, sort= TRUE) %>%
  rename("Response" = "Interseed")
  
```

```{r}
Q4_plot = Q4 %>%
  ggplot(aes(x = Response, y = n, fill= Response, label= n)) +
  geom_col() +
  geom_text(nudge_y= 2) +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  labs(title= "Why do you plant (recommend planting) cover crops into or after corn silage/grain? (Mark all that apply)") +
  coord_flip()

Q4_plot
#Doesn't work well because of many responses with combined answers
```

# Which cover crop species do you plant (recommend planting) after corn silage harvest? (Circle all that apply)
```{r}
Q5 = data1 %>%
  count(After, sort= TRUE) %>%
  rename("Response" = "After")
  
```

```{r}
Q5_plot = Q5 %>%
  ggplot(aes(x = Response, y = n, fill= Response, label= n)) +
  geom_col() +
  geom_text(nudge_y= 2) +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  labs(title= "Why do you plant (recommend planting) cover crops into or after corn silage/grain? (Mark all that apply)") +
  coord_flip()

Q5_plot
#Doesn't work well because of many responses with combined answers
```

# Agree or Disagree More research is needed on early interseeding of cover crops into corn (pre-V6).
```{r}
Q6 = data1 %>%
  count(Early, sort= TRUE) %>%
  rename("Response" = "Early")
  
```

```{r}
Q6_plot = Q6 %>%
  ggplot(aes(x = Response, y = n, fill= Response, label= n)) +
  geom_col() +
  geom_text(nudge_y= 2) +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  labs(title= "Agree or Disagree More research is needed on early interseeding of cover crops into corn (pre-V6).") +
  coord_flip()

Q6_plot
```

# Agree or Disagree More research is needed on late interseeding of cover crops into corn (post tasseling).
```{r}
Q7 = data1 %>%
  count(Late, sort= TRUE) %>%
  rename("Response" = "Late")
  
```

```{r}
Q7_plot = Q7 %>%
  ggplot(aes(x = Response, y = n, fill= Response, label= n)) +
  geom_col() +
  geom_text(nudge_y= 2) +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  labs(title= "Agree or Disagree More research is needed on late interseeding of cover crops into corn (post tasseling).") +
  coord_flip()

Q7_plot
```


# Which method of late season interseeding, if any, should researchers focus on? (Circle all that appl
```{r}
Q8 = data1 %>%
  count(Method, sort= TRUE) %>%
  rename("Response" = "Method")
  
```

```{r}
Q8_plot = Q8 %>%
  ggplot(aes(x = Response, y = n, fill= Response, label= n)) +
  geom_col() +
  geom_text(nudge_y= 2) +
  theme(axis.title.y = element_blank(),
        legend.position = "none") +
  labs(title= "Agree or Disagree More research is needed on late interseeding of cover crops into corn (post tasseling).") +
  coord_flip()

Q8_plot
```

#Word cloud
```{r}
library(ggwordcloud)

wc_plot = Q3 %>%
  ggplot(aes(label= Response, size= n, color= Response)) +
  geom_text_wordcloud() +
  theme_minimal()
wc_plot
```















